TacticToe: Learning to Prove with Tactics

### 2018-08-22 tactictoe_jv.tex
portability

\paragraph{Portability}
Although \tactictoe is designed for \holfour, the ideas presented could be 
ported to another ITP. We highlight here the major modules of \tactictoe  some 
of the hurdles that developers might encounter during their re-implementation 
for another ITP:
\begin{itemize}
	\item A recording mechanism that can extract context-independent tactics 
	and the goal they were trying to solve. In our implementation, few tactics 
	are stateful and they usually become more powerful over time.
	\item Efficient tactics:
	\item Efficient predictors
	\item Efficient search: 
	 the MCTS algorithm should be re-implemented in the language of the 
	ITP, because better integration improves the efficiency of the algorithm.

\end{itemize}

>>>>

\paragraph{Portability}
Although \tactictoe is designed for \holfour, the \tactictoe modules 
implemented in this paper could be ported to another ITP. In order to 
facilitate this work, we give
ideas on how to adapt the major components of \tactictoe in the context of 
another ITP and warn about some of the issues that could arise during this work.
First, the recording mechanism requires the ability to parse and manipulate 
proof scripts and include the possibility to define and recognize what a tactic 
is. In \holfour, \sml is our proof scripts language, so this was achieved by 
parsing the \sml programming language. In other ITPs, this task may be 
facilitated by the fact that proof scripts are written with a specifically 
designed language so the ability to modify syntax trees of proof scripts may 
already be available. Another issue that can negatively impact the quality of 
the recorded data is the fact that the effect of the tactics may depend on the 
state of the ITP (i.e. flags), which rarely happens in \holfour. If the 
behavior of a tactic drastically changes under different context, then the part 
of the context that affects it should become part of the tactic.
Porting the other modules (abstraction, orthogonalization, predictors and MCTS 
search) should be quite straightforward. Provided that application of 
tactics and the computation of predictions is fast enough (in the order of 
10 milliseconds each), the MCTS algorithm should explore enough of the tactic 
space to be a valuable tool for theorem proving.
